---
title: "Control data analysis workbook for Arsenolipid MS"
author: "Katherine Heal"
date: "March 16 2021"
output: html_document
---

# Database creation 
Create an MS1 database for AsHC, AsFA, AsSugPL, lysoAsSugPL, AsPC (single and double charges are different right now) and a few extras, split it up into smaller and larger masses to use for the inclusion list
```{r, warning=FALSE, message = FALSE}
# Inputs are "MetaData/DB_construction.csv", output is "MetaData/AsLipidDatabase/full_MS1db.csv" and inclusion lists for QE analysis

source("SourceCode/database_construction.R")
remove(list = ls())
```

# Extract and merge MS2 data in preparation for analysis
This takes a long time (with retention time window of 20 s). It pulls out the MS2s from the DDA .mzxml files and merges several scans (with a rt window of 20s) with matching precurors. Writes out 
Only needs to be run again if we decide to merge differently
```{r, warning=FALSE, message = FALSE}
# Inputs are all the .mzxml files within the folder ""RawDat/20201026_QE_secondLipidRun", output is rdata saved into the "RawDat/20201026_QE_secondLipidRun" folder as _mergedMS2s
source("SourceCode/MS2_extractor.R")
remove(list = ls())
```

# Data analysis chunks
## Tidy up ICAP data
This code takes in combined .csv files from the ICAP (with Y and time), tidies them up a bit and writes out new files and writes them in to the pivoted folder within rawdat
```{r, warning=FALSE, message = FALSE}
# Inputs are four files within "RawDat/ICAP_run_20200901" (straight from ICAP), output as "RawDat/ICAP_run_20200901/Pivoted/" for further analysis
source("SourceCode/extract_and_organize_ICAPdata09012020.R") #bulk As data
source("SourceCode/extract_and_organize_ICAPdata201026.R") #second run of Aslipids
remove(list = ls())
```

## Calculate bulk arsenic concentrations
```{r}
# Inputs are pivoted from extract_and_organize_ICAPdata09012020.R and metadat, output is "Intermediates/bulk_quantification.csv"
source("SourceCode/concentrations_of_bulk_samps.R")
remove(list = ls())
```


## Do baseline and save out results from that correction
```{r, warning=FALSE, message = FALSE}
# Does baseline, peak detection, and smoothing of ICP data, then gets detected peaks,  Inputs are pivoted "RawDat/ICAP_run_20200901/Pivoted/", Outputs are Intermediates/Baseline_CSVs/", one file per sample
source("SourceCode/do_baseline_calculation.R") 
remove(list = ls())

```

## Calculate 75As concentration in lipids from ICAP data
Gets peak areas of As peaks in ICPMS data files
Writes this out into Intermediates/AsLipids_ICPpeakareas.csv
```{r, warning=FALSE, message = FALSE}
# Get area of cobalt standards for RF
source("SourceCode/standard_area_extraction.R")
remove(list = ls())


# Gets under-the-hump area and concentrations for all samples
source("SourceCode/under_the_hump_areas.R")
remove(list = ls())


# Gets concentrations of identified peaks from all samples
source("SourceCode/better_peak_areas.R")
remove(list = ls())

```

