---
title: "Control data analysis workbook"
output: html_notebook
---

# Data analysis chunks
## Tidy up ICAP data
This code takes in combined .csv files from the ICAP (with Y and time), tidies them up a bit and writes out new files and writes them in to the pivoted folder within rawdat
```{r, warning=FALSE, message = FALSE}
source("SourceCode/extract_and_organize_ICAPdata09012020.R")
```

## Calculate bulk concentrations
Calculates the bulk concentrations of the environmental samples
Writes this out into Intermediates/ 
```{r, warning=FALSE, message = FALSE}
source("SourceCode/extract_and_organize_ICAPdata09012020.R")
```
#
# Figures
## Standard curve figures
Writes 2 figures into Figures/ManuscriptReady
```{r, warning=FALSE, message = FALSE}
source("Figures/Rcode/Std_curves.R")
```

## Preliminary figure of lipid ICAP chromats
Writes 1 figures into Figures/Preliminary
```{r, warning=FALSE, message = FALSE}
source("Figures/Rcode/Lipid_Exploratory_Plots.R")
```
#
# Tables
## Sample overview
Writes sample overview table into Tables/ManuscriptReady
```{r, warning=FALSE, message = FALSE}
source("Tables/Rcode/Sample_descriptions.R")
```

## Table of bulk concentrations
Working on this as of 10/12/20
```{r, warning=FALSE, message = FALSE}
source("Tables/Rcode/Quantitative_overview.R")
```
#