---
title: "Exploration and preliminary data analysis workbook for Arsenolipid MS"
author: "Katherine Heal"
date: "March 16 2021"
output: html_document
---
These scripts were crucial for finding peaks in the HRESIMS data using the MS1 and MS2 databases

## Targeted Search, plots MS1, MS1 of C13 (scaled), and MS2 (if it picked)
Saves each sample as a PDF in Intermediates/ with all possible hits from the MS1 database
```{r, warning=FALSE, message = FALSE}
source("SourceCode/targeted_search.R")
```

## Targeted Search based on MS2 only
Saves each sample as a PDF in Intermediates/ with all possible hits from the MS2 database that were not picked from the MS1 search
```{r, warning=FALSE, message = FALSE}
source("SourceCode/targeted_search_MS2work.R")
```

# This does a preliminary search for peaks in the ICPMS data, which I later manually inspected  
```{r, warning=FALSE, message = FALSE}
# Does baseline, peak detection, and smoothing of ICP data, then gets detected peaks
source("SourceCode/get_peak_areas_201026.R") 
```

## Put identifications on the peaks to get 
Writes "Intermediates/IDd_Lipids_IDd.csv"
This isn't used from here on out - just used this to get good ids initially which were confirmed and saved in "MetaData/Targeted_visually_IDd_2.csv"
```{r, warning=FALSE, message = FALSE}
source("SourceCode/identification_of_quantified_peaks.R")
```



