---
title: "Make your figures here"
author: "Katherine Heal"
date: "January 10 2020"
output: html_document
---
Figures for particulate arsenic manuscript and associated presentations

```{r setup, include=FALSE}
library(tidyverse)
```

# Figure with lipid ICP traces for all 4 samples
Shows which lipids we IDd, other non-IDd lipids too
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Rcode/ICP_trace_plots.R')
remove(list = ls())
```

# Figure with example ICP, MS1, MS2 from AsSugPL954 (from PS1), AsHC (from BATS), unknown early (from ALOHA), and unknown late (from PS3)
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Rcode/Example_individual_lipids.R')
remove(list = ls())
```

# Figure with list of lipids, names, mz, time, Y/N concentration for each sample
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Rcode/Lipid_sample_tile.R')
```














# Standard curve plots
```{r, error = FALSE, warning=FALSE, message=FALSE}
source('Figures/Rcode/Std_curves.R')
remove(list = ls())
```




# Figures for each individual lipid in each sample (targeted)
```{r, error = FALSE, warning=FALSE, message=FALSE}
# High mass lipids
source('Figures/Rcode/Individual_lipid_plots.R')

# Low mass lipids
source('Figures/Rcode/Individual_lipid_plots_lowmass.R')

# ALOHA unknowns
source('Figures/Rcode/Example_individual_lipids_unknowns_ALOHA.R')

# PS3 unknowns
source('Figures/Rcode/Example_individual_lipids_unknowns_PS2.R')

```

